\documentclass[./main.tex]{subfiles}
\begin{document}

Gaitsgory-Rozenblyum has a highly abstract but clean definition of
dg-categories, which can be summarised in the following diagram : 
% \begin{cd}
% 	& {(\infty,1)\text{-}\mathrm{Cat}} & {(\infty,1)\text{-}\mathrm{Cat}^\mathrm{ex}} & {\mathrm{Vec}^\mathrm{f.d.}\text{-}\mathrm{Mod}} \\
% 	{} & {} & {(\infty,1)\text{-}\mathrm{Cat}^\mathrm{ex}_\mathrm{cts}} & {\mathrm{Vec}\text{-}\mathrm{Mod}} \\
% 	& {} & {} & {}
% 	\arrow[from=1-3, to=1-2]
% 	\arrow[from=1-4, to=1-3]
% 	\arrow[from=2-3, to=1-3]
% 	\arrow[from=2-4, to=1-4]
% 	\arrow[from=2-4, to=2-3]
% \end{cd}
% https://q.uiver.app/?q=WzAsOCxbMSwwLCIoXFxpbmZ0eSwxKVxcdGV4dHstfVxcbWF0aHJte0NhdH0iXSxbMiwwLCIoXFxpbmZ0eSwxKVxcdGV4dHstfVxcbWF0aHJte0NhdH1eXFxtYXRocm17ZXh9Il0sWzMsMCwiXFxtYXRocm17VmVjfV5cXG1hdGhybXtmLmQufVxcdGV4dHstfVxcbWF0aHJte01vZH0iXSxbMSwyLCIoXFxpbmZ0eSwxKVxcdGV4dHstfVxcbWF0aHJte0NhdH1eXFxtYXRocm17UHJ9X0wiXSxbMiwyLCIoXFxpbmZ0eSwxKVxcdGV4dHstfVxcbWF0aHJte0NhdH1eXFxtYXRocm17ZXh9X1xcbWF0aHJte2N0c30iXSxbMywyLCJcXG1hdGhybXtWZWN9XFx0ZXh0ey19XFxtYXRocm17TW9kfSJdLFsxLDEsIlxcbWF0aHJte0FjY30iXSxbMCwxLCJcXG1hdGhybXtBY2N9X1xca2FwcGEiXSxbMSwwXSxbMiwxXSxbNiwwXSxbMyw2XSxbNCwzXSxbNSw0XSxbNCwxXSxbNSwyXSxbNyw2XSxbNywwLCIiLDEseyJvZmZzZXQiOjF9XSxbMCw3LCJcXG1hdGhybXtJbmR9X1xca2FwcGEiLDIseyJsYWJlbF9wb3NpdGlvbiI6NzAsIm9mZnNldCI6NSwic2hvcnRlbiI6eyJzb3VyY2UiOjIwfX1dLFs3LDAsIlxcYm90IiwxLHsib2Zmc2V0IjotMiwic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoibm9uZSJ9LCJoZWFkIjp7Im5hbWUiOiJub25lIn19fV1d
\begin{cd}
	{\mathrm{Set}} & {1\text{-}\mathrm{Cat}} & {\mathrm{Cat}_\mathrm{dg} k} \\
	{\mathrm{Spc}} & {(\infty,1)\text{-}\mathrm{Cat}} & {(\infty,1)\text{-}\mathrm{Cat}^\mathrm{ex}} & {\mathrm{Vec}^c\text{-}\mathrm{Mod}} & {\mathrm{DGCat}} \\
	& {} & {(\infty,1)\text{-}\mathrm{Cat}^\mathrm{ex}_\mathrm{cts}} & {\mathrm{Vec}\text{-}\mathrm{Mod}} & {\mathrm{DGCat}_\mathrm{cts}}
	\arrow[from=2-1, to=2-2]
	\arrow[from=1-1, to=2-1]
	\arrow[from=1-1, to=1-2]
	\arrow["N"', shift right=2, from=1-2, to=2-2]
	\arrow["h"', shift right=2, from=2-2, to=1-2]
	\arrow["\vdash"{description}, draw=none, from=1-2, to=2-2]
	\arrow[from=2-3, to=2-2]
	\arrow["{N_\mathrm{dg}}", from=1-3, to=2-3]
	\arrow[from=3-3, to=2-3]
	\arrow[from=3-4, to=3-3]
	\arrow[from=2-4, to=2-3]
	\arrow[from=3-4, to=2-4]
	\arrow["{=:}"{description}, draw=none, from=3-5, to=3-4]
	\arrow["{=:}"{description}, draw=none, from=2-5, to=2-4]
\end{cd}
Some explanations are due :  
\begin{itemize}
  \item We will use ``infinity category'' to refer only to 
  $(\infty,1)$-categories.
  The word ``category'' will exclusively refer to $1$-categories.

  $(\infty,1)\dash\CAT$ denotes the infinity category of 
  small infinity categories. 
  $(\infty,1)\dash\CAT$ has all small limits (Kerodon 7.4.1.11)
  and small colimits (Kerodon 7.4.3.13) and
  is cartesian closed.
  We use $\FUN(C,D)$ to denote the infinity category of functors from
  $C$ to $D$.

  There is an adjunction 
  $h \dashv N : (\infty,1)\dash\CAT \rightleftarrows 1\dash\CAT$.
  $N$ is called the \emph{nerve functor} and it is fully faithful,
  allowing us to see 1-categories as $\infty$-categories.
  In particular, we use $\De^n$ to denote the \emph{$n$-simplex},
  the $\infty$-category obtained from the linear order
  $[n] = \set{0 \leq \cdots \leq n}$.
  Given an infinity category $C$,
  objects of $C$ are the same as functors $\De^0 \to C$
  and morphisms in $C$ are the same as functors $\De^1 \to C$.

  There is a full subcategory $\SPC$ of $(\infty,1)\dash\CAT$ consisting
  of $\infty$-categories $X$ where all morphisms are isomorphisms.
  These are called \emph{$\infty$-groupoids} but also \emph{spaces}
  by homotopy theorists.
  The infinity category $\SPC$ plays the role of $\SET$ in 1-category theory
  in the sense that given an infinity category $C$,
  the fiber of $\FUN(\De^1 , C) \to \FUN(\partial\De^1 , C)$
  over $(X,Y)$, denoted $C(X,Y)$, is in fact a space.
  The nerve functor $N$ lands $\SET$ inside $\SPC$,
  where given a set $S$ and two points $x, y \in S$,
  we have $NS(x,y) \simeq \nothing$ the empty space.
  In other words, sets are ``discrete spaces''.

  For any infinity category $C$, 
  we define $\PSH\,C := \FUN(C\op,\SPC)$ and refer to its objects as
  \emph{presheaves in $C$}.
  Infinity categories of presheaves are significant since
  we will be working with derived algebraic geometry functorially.
  We will use the following universal property of $\PSH\,C$ many times.

  \link{dgcat.psh.up}
  \begin{prop}[Universal Property of Presheaf $\infty$-Categories]

    Let $S$ be a small $\infty$-category.
    \begin{itemize}
      \item There is a fully faithful functor $S \to \PSH\,S$
      which takes each object $x$ in $S$ to the functor 
      $S(\_ , x) : C\op \to \SPC$ taking points $y$ to $S(y,x)$.
      This is called the \emph{Yoneda embedding}.
      \item (Lurie HTT 5.1.2.3) 
      $\PSH\,S$ has small colimits and small limits.
      In fact, they are computed pointwise.
      \item (Lurie HTT 5.1.5.6 and 5.2.6.5) 
      For $C$ be an $\infty$-category with small colimits, 
      let $\mathrm{Fun}^L(\PSH\, S , C)$ denote the
      full subcategory of $\mathrm{Fun}(\PSH\, S, C)$ consisting of
      functors preserving small colimits.
      Then restricting along the Yoneda embedding $S \to \PSH\, S$
      gives an equivalence of $\infty$-categories : 
      \[
        \mathrm{Fun}^L(\PSH\, S , C) \map{\sim}{} \mathrm{Fun}(S , C)  
      \]
      An inverse functor is given by left Kan extension.
      In particular,
      for $u_! \in \mathrm{Fun}^L(\PSH\, S , C)$ corresponding to 
      $u \in \mathrm{Fun}(S , C)$,
      we have for every $X \in \PSH\, S$ that
      $u_!$ exhibits $u_!(X)$ as the colimit of the diagram 
      $S_{/ X} \to S \to C$.
      Furthermore, if we assume $C$ is locally small,
      then we have an adjunction 
      \[
        u_! \dashv u^* : \PSH\,S \rightleftarrows C
      \]
      where $u^*$ is given by the composition 
      \[
        C \map{\text{Yoneda}}{} \PSH\,C = \FUN(C,\SPC^\OP) 
        \map{\text{restrict along $u$}}{} \FUN(S,\SPC^\OP) = \PSH\,S
      \]
    \end{itemize}
  \end{prop}

  An immediate consequence of the above is the following,
  which is key for defining de Rham spaces.

  \link{dgcat.psh.triple}
  \begin{lem}[Left and Right Kan Extensions of Presheaves]
    
    Let $u : S \to T$ be a functor between small $\infty$-categories.
    Then we have a triple of adjoints : 
    \begin{cd}
      {\mathrm{PSh}\,S} & {} & {\mathrm{PSh}\,T}
      \arrow["{u^*}"{description}, from=1-3, to=1-1]
      \arrow["{\mathrm{u_!}}", shift left=5, from=1-1, to=1-3]
      \arrow["{u_*}"', shift right=5, from=1-1, to=1-3]
      \arrow["\bot"{description}, shift left=3, draw=none, from=1-1, to=1-3]
      \arrow["\bot"{description}, shift right=3, draw=none, from=1-1, to=1-3]
    \end{cd}
    where 
    \begin{itemize}
      \item $u_!$ is the left Kan extension of $S \to T \to \PSH\,T$
      \item $u^*$ is the composition $\PSH\,T \to \PSH\,\PSH\,T \to \PSH\,S$
      \item $u_*$ is the composition $\PSH\,S \to \PSH\,\PSH\,S \to \PSH\,T$
    \end{itemize}
    In particular, for $X \in \PSH\,S$,
    $u_!(X)$ is the left Kan extension of $X$ along $S \to T$
    and $u_*(X)$ is the right Kan extension of $X$ along $S \to T$.
    \begin{proof1}
      For $u_! \dashv u^*$, we apply the universal property of
      presheaf $\infty$-categories to $S \to T \to \PSH\,T$.
      Now for $u^* \dashv u_*$, note that
      since colimits in $\PSH\,T$ are computed pointwise,
      we have that $u^*$ preserves small colimits.
      This means we can apply the universal property of 
      presheaf $\infty$-categories again,
      but this time to the composition $T \to \PSH\,T \to \PSH\,S$.
      This gives $u^* \dashv u_*$. 
    \end{proof1}
  \end{lem}

  \item $(\infty,1)\dash\CAT^\mathrm{ex}$ denotes subcategory of $1\dash\CAT$
  consisting of \emph{stable infinity categories} and \emph{exact functors}.  
  It contains all small limits and
  the ``inclusion'' $1\dash\CAT^{ex} \to 1\dash\CAT$ preserves 
  small limits (Lurie HA 1.1.4.4).

  Stable infinity categories are basically
  triangulated categories where exact triangles are determined by
  an infinity-categorical universal property.
  Here is the definition.
  \begin{dfn}
    
    Let $C$ be an infinity category. 
    We say $C$ has a \emph{zero object} when
    it has an object that is both initial and final. 
    (Lurie HA 1.1.1.1.)

    Now assume $C$ have a zero object.
    Then a \emph{triangle} in $C$ is defined as a diagram in $C$ of the form : 
    \begin{cd}
      X & Y \\
      0 & Z
      \arrow[from=1-1,to=1-2]
      \arrow[from=1-1,to=2-1]
      \arrow[from=1-2,to=2-2]
      \arrow[from=2-1,to=2-2]
    \end{cd}
    A triangle is called a \emph{fiber sequence} when it is a cartesian
    and a \emph{cofiber sequence} when it is cocartesian.
    (Lurie HA 1.1.1.4.)
    In the first case,
    we say \emph{$Y \to Z$ admits a kernel} and refer to $X$ as the kernel,
    and in the other case
    we say \emph{$X \to Y$ admits a cokernel} and refer to $Z$ as the cokernel.
    \footnote{
      In Lurie HA,
      kernels are called fibers and cokernels are called cofibers.
    }

    $C$ is called \emph{stable} when the following are true : 
    \begin{itemize}
      \item every morphism has both a kernel and a cokernel.
      \item A triangle is fiber sequence iff it is a cofiber sequence.
      Such triangles are called \emph{exact triangles}.
    \end{itemize}
    (Lurie HA 1.1.1.9.)

    An exact functor $F : C \to D$ between stable infinity categories
    is one which satisfy any of the following equivalent conditions : 
    (Lurie HA 1.1.4.1)
    \begin{itemize}
      \item $F$ preserves exact triangles
      \item $F$ preserves finite limits
      \item $F$ preserves finite colimits.
    \end{itemize}
    
    For stable $\infty$-categories $C, D$
    the full subcategory $\FUN^\EX(C,D)$ of $\FUN(C,D)$ consisting of
    exact functors is also stable.\footnote{
      GRI Chapter 1 5.1.4 claims this.
      Lurie HA 1.1.3.1 shows that $\FUN(K,C)$ is stable for
      any $K$ and stable $C$.
      The result follows given that
      finite (co)limit-preserving functors
      are closed under finite (co)limits.
    }
  \end{dfn}
  To help build intuition of ``stable infinity categories as 
  fixed triangulated categories'',
  we record here the important parts of the procedure
  of extracting a triangulated category from a stable infinity category.
  \begin{prop}[Lurie 1.1.2.14]
    
    Let $C$ be a stable infinity category.
    Then the following defines a triangulated structure on 
    the 1-category $hC$ : 
    \begin{itemize}
      \item Define the \emph{suspension functor} $\Sigma : C \to C$ by
      pushout against zeros : 
      \begin{cd}
        X & 0 \\
        0 & \Sigma X
        \arrow[from=1-1,to=1-2]
        \arrow[from=1-1,to=2-1]
        \arrow[from=1-2,to=2-2]
        \arrow[from=2-1,to=2-2] 
      \end{cd}
      Since the above square is a cofiber sequence,
      it is also a fiber sequence. 
      This shows that \emph{looping} $\Omega : C \to C$,
      given by pullback against zeros, gives an inverse for $\Sigma$
      and hence shows that $\Sigma$ is an equivalence.
      Taking homotopy categories, we obtain an equivalence 
      $[1] : hC \map{\sim}{} hC$, which we use as the shift functor
      for the triangulated structure.

      \item We call a diagram \[
        X \map{f}{} Y \map{g}{} Z \map{h}{} X[1] 
      \]
      in $hC$ an exact triangle (in the triangulated categorical sense) 
      when it comes from a diagram of the following form in $C$ : 
      \begin{cd}
        X & Y & 0 \\
        0 & Z & {X[1]}
        \arrow[from=1-1, to=1-2]
        \arrow[from=1-2, to=2-2]
        \arrow[from=2-2, to=2-3]
        \arrow[from=1-1, to=2-1]
        \arrow[from=2-1, to=2-2]
        \arrow[from=1-2, to=1-3]
        \arrow[from=1-3, to=2-3]
        \arrow["\lrcorner"{anchor=center, pos=0.125, rotate=180}, 
          draw=none, from=2-2, to=1-1]
        \arrow["\lrcorner"{anchor=center, pos=0.125, rotate=180}, 
          draw=none, from=2-3, to=1-2]
      \end{cd}
      i.e. two exact triangles (in the stable infinity categorical sense).
      \item For $X, Y$ objects of $C$,
      we have 
      \begin{align*}
        C(X,Y) &\simeq C(\Sigma \Omega X , Y) \simeq \Omega C(\Omega X , Y) \\
        &\simeq C(\Sigma^2 \Omega^2 X , Y) \simeq \Omega^2 C(\Omega^2 X , Y)
      \end{align*}
      Upon taking $\pi_0$ , we obtain 
      \[
        hC(X,Y) := \pi_0 C(X,Y) \simeq \pi_1 C(\Om X , Y) 
        \simeq \pi_2 (\Om^2 X , Y)
      \]
      where the last isomorphism is a group morphism.
      For $\pi_2$ of any ``space'' \footnote{
        In the quasi-category model of infinity categories,
        $C(X,Y)$ is a Kan complex,
        which one can take homotopy groups of.
      } the obvious group structure given by is abelian,
      this gives $hC(X,Y)$ an abelian group structure,
      making $hC$ into an additive category.
    \end{itemize}

    For $X, Y$ objects in $C$,
    we define the abelian group $\EXT^n_C(X,Y) := hC(X , Y[n])$.
    (Lurie HA 1.1.2.17)
  \end{prop}

  (IP : t-structures, truncation as reflective localisation,
  $(D^-(A))^\heartsuit \simeq A$ Lurie 1.3.2.19)

  \begin{dfn}
    
    Let $F : C \to D$ be a functor in $1\dash\CAT^\EX$
    where $C$ and $D$ are equipped with t-structures.
    Then $F$ is called \emph{right t-exact} when
    $F C_{0 \leq} \subs D_{0 \leq}$.
    It is called \emph{left t-exact} when $F C_{\leq 0} \subs D_{\leq 0}$.
    We say $F$ is \emph{t-exact} when it is both left and right t-exact. 

  \end{dfn}

  \item We are now ready for compactly generated $\infty$-categories.
  We will only make use of the case of 
  \emph{stable} compactly generated $\infty$-categories
  since many definitions then admit alternative characterisations
  which can be checked at the level of triangulated categories.

  We first note that the theory of colimits
  simplifies in the stable case.
  \begin{prop}[Lurie HA 1.4.4.1]
    
    \begin{itemize}
      \item For a stable $\infty$-category $C$, TFAE: 
      \begin{itemize}
        \item admitting small colimits
        \item admitting small filtered colimits
        \item admitting small coproducts
      \end{itemize}
      \item For a functor $F : C \to D$ between stable $\infty$-categories
      which admit small colimits, TFAE: 
      \begin{itemize}
        \item preserving small colimits
        \item preserving small filtered colimits
        \item preserving small coproducts
      \end{itemize}
      Any functor satisfying the above, GR calls \emph{continuous}.
    \end{itemize}
  \end{prop}
  
  We now explain compact generation.
  The starting point is the theory of \emph{inductive completions}\footnote{
    This is a bit of a misnomer because 
    intuitively we are adding filtered \emph{colimits}, not limits.
  }.
  Here are the main results concerning ind-completions in the stable case.
  \begin{prop}[Ind-completions of Stable $\infty$-Categories]
  
    Let $C$ be a small $\infty$-category and $\ka$ a regular cardinal.\footnote{
      A regular cardinal $\ka$ is a cardinality that is 
      ``sufficiently large'' in the sense that
      the 1-category $\SET_{<\ka}$ of sets with cardinality strictly less than
      $\ka$ has all colimits of size strictly less than $\ka$.
      The cardinality of $\N$ is an example, 
      since a finite colimit of finite sets is still finite.
    }
    Then the Yoneda embedding $C \to \PSH\,C$ factors through a full subcategory
    $\IND_\ka(C)$ with the following properties : 
    \begin{itemize}
      \item (Lurie HTT 5.3.5.3) 
      $\IND_\ka(C)$ has all small $\ka$-filtered colimits
      and the inclusion $\IND_\ka(C) \subs \PSH\, C$ preserves them
      \item (Lurie HTT 5.3.5.4) 
      An object $X$ in $\PSH\,C$ is in $\IND_\ka(C)$ iff
      it is a $\ka$-filtered colimit of representables iff
      $X : C\op \to \SPC$ preserves $\ka$-small limits.
      \item (Lurie HA 1.1.3.6) If $C$ is stable then so is $\IND_\ka(C)$.
      \item (Lurie HTT 5.3.5.10) For any $\infty$-category $D$ 
      admitting small $\ka$-filtered colimits,
      we have the following equivalence of functor $\infty$-categories : 
      \[
        \FUN_\ka(\IND_\ka(C) , D) \map{\sim}{} \FUN(C , D)
      \]
      where \begin{itemize}
        \item the left category denotes the full subcategory of 
        $\FUN(\IND_\ka(C),D)$ consisting of functors preserving 
        $\ka$-filtered colimits.\footnote{
          At Lurie HTT 5.3.4.5, 
          these are called $\ka$-continuous functors.
          Taking the minimal case of $\ka = \abs{\N}$,
          it seems only reasonable to refer to 
          functors preserving filtered colimits as
          \emph{continuous} functors.
          This is a potential explanation of GR's choice of terminology
          for continuous functors.
        }
        \item the forward functor is given by restricting along the Yoneda embedding 
        $C \to \IND_\ka(C)$
        \item the inverse functor is given by left Kan extension.
      \end{itemize} 
      Assuming $C, D$ are stable and $\ka$ is the cardinality of $\N$, 
      the above equivalence restricts to
      an equivalence between the following two full subcategories :
      \[
        \FUN_\CTS^\EX(\IND_\ka(C) , D) \map{\sim}{} \FUN^\EX(C , D)
      \]
      where the left is the $\infty$-category of
      exact continuous functors from $\IND_\ka(C)$ to $D$.

    \end{itemize}

    When $\ka$ is the cardinality of $\N$,
    we write $\IND$ instead of $\IND_\ka$.
  \end{prop}
  
  For a regular cardinal $\ka$ and an $\infty$-category $C$,
  we say $C$ is $\ka$-compactly generated when
  it has all small colimits and there exists a small $\infty$-category
  $C^0$ with an equivalence $\IND_\ka(C^0) \map{\sim}{} C$.\footnote{
    This is unraveled from Lurie HTT 5.5.7.1, 5.5.0.18, and 5.4.2.1.
    In particular, the second condition is usually called 
    $\ka$-accessibility, but we have no need for such terminology.
  }
  For the case of $\ka =$ cardinality of $\N$,
  we simply say \emph{compactly generated}.
  A \emph{presentable} $\infty$-category is one that is
  $\ka$-compactly generated for some $\ka$.
  We use $(\infty,1)\dash\CAT^\EX_\CTS$ to denote
  the subcategory of $(\infty,1)\dash\CAT^\EX$ whose objects are
  presented stable $\infty$-categories and morphisms are
  exact functors preserving small coproducts.

  One appeal of presentable stable $\infty$-categories is that
  we have the adjoint functor theorem at our disposal.
  \begin{prop}[Adjoint Functor Theorem for Presentable $\infty$-Categories
    (Lurie HTT 5.5.2.9)]
    
    Let $F : C \to D$ be a functor between presentable $\infty$-categories.
    \begin{itemize}
      \item $F$ is a left adjoint iff it preserves small colimits.
      \item Assuming $C, D$ are $\ka$-compactly generated,
      $F$ is a right adjoint iff it preserves small limits and
      $\ka$-filtered colimits.
    \end{itemize}
  \end{prop}

  For functors out of $\IND_\ka(C)$,
  fully faithfulness and equivalence can be detected at the level of $C$.
  \begin{prop}[Functors out of Compactly Generated Categories
    (Lurie 5.3.5.11)]
    
    Let $C^0$ be a small $\infty$-category, $\ka$ a regular cardinal,
    $C = \IND_\ka(C^0)$ and
    $D$ an $\infty$-category admitting $\ka$-filtered colimits.
    Let $D^\ka$ be the full subcategory of $D$ consisting of 
    $\ka$-compact objects.
    Let $F : C \to D$ be a functor preserving $\ka$-filtered colimits
    and $F_0 : C^0 \to D$ its restriction along 
    the Yoneda embedding $C^0 \to C$.
    \begin{itemize}
      \item If $F_0$ is fully faithful and its essential image lands in $D^\ka$,
      then $F$ is fully faithful.
      \item $F$ is an equivalence iff the following are true :
      \begin{itemize}
        \item $F_0$ fully faithful
        \item $F_0$ factors through $D^\ka$
        \item all objects of $D$ are $\ka$-filtered colimits of diagrams
        in $D$ with objects in the image of $F_0$.
      \end{itemize}
      In particular,
      for any full subcategory $\tilde{C} \subs C^\ka$ which
      generates $C$ under $\ka$-filtered colimits,
      we have $\IND_\ka(\tilde{C}) \map{\sim}{} C$.
    \end{itemize}
  \end{prop}

  Furthermore, 
  the Yoneda embedding $C^0 \to C$ factors through $C^\ka$.
  The fully faithful functor $C^0 \to C^\ka$ is not in general an equivalence,
  however it does exhibit $C^\ka$ as the \emph{idempotent completion}
  of $C^0$.
  (Lurie 5.4.2.4.)
  So if $C^0$ is idempotent complete, 
  then we recover the $\ka$-compact objects of $C$ as precisely 
  (the essential image of) $C^0$.
  One doesn't need to know the general $\infty$-categorical definition for 
  idempotent completion since we will only be in the stable setting,
  in which we have the following characterisation.
  \begin{prop}[Idempotent Completeness in Stable Case (Lurie HA 1.2.4.6)]
    
    Let $C$ be a stable $\infty$-category.
    Then $C$ is idempotent complete iff $hC$ is as a 1-category,
    i.e. for every morphism $e : B \to B$ such that $e^2 = e$,
    there exists a retract of $s : A \rightleftarrows B : r$
    that exhibits $e = r s$.

    If the above is the case,
    then for any regular cardinal $\ka$ we have
    $C \map{\sim}{} (\IND_\ka(C))^\ka$.
  \end{prop}

  One should not worry about having to check presentability of
  a stable $\infty$-category since all the computable examples
  are in the compactly generated case.
  As it turns out, this can be checked at the level of 
  the triangulated categories.
  \begin{prop}[Compact Generation of Stable Infinity Categories]
    
    Let $C$ be a stable $\infty$-category.
    We say an object $X$ \emph{generates $C$} when
    for all objects $Y$ in $C$, 
    $hC (X,Y) = 0$ implies $Y \simeq 0$.
    Then the following are true : 
    \begin{enumerate}
      \item Suppose we have that :
      \begin{itemize}
        \item $C$ has small coproducts
        \item $hC$ is locally small
        \item There exists a compact object $X$ which generates $C$.
      \end{itemize}
      Define the following sequence of full subcategories of $C$ : 
      \begin{align*}
        C(0) &:= 
          \text{full subcategory of $C$ spanned by $\set{X[n]}_{n \in\Z}$} \\
        C(k + 1) &:= 
          \text{full subcategory of $C$ spanned by finite colimits of 
          objects in $C(k)$} \\
        C(\om) &:= \bigcup_{n \in \N} C(n) 
      \end{align*}
      Then $C(\om)$ equivalent to a small $\infty$-category and 
      $\IND\,C(\om) \map{\sim}{} C$.
      In particular, $C$ is compactly generated.
      \item (Lurie HA 1.4.4.1) For an object $X$ in $C$,
      $X$ is compact if and only if for every morphism 
      $f : X \to \coprod_{i \in I} Y_i$ in $C$,
      there exists a finite subset $I_0 \subs I$ such that
      in $hC$, $f$ factors through 
      $\coprod_{i \in I_0} Y_i \to \coprod_{i \in I} Y_i$.
    \end{enumerate}
  \end{prop}
  \begin{proof}
    We omit the proof of (2).
    The following proof of (1) is extracted from the proof of Lurie HA 1.4.4.2.

    Showing $C(\om)$ is equivalent to a small $\infty$-category
    is a set-theoretic issue that's not very interesting,
    so we will use the following result without proof.
    \begin{lem}

      Let $C$ be an $\infty$-category and $\ka$ a regular cardinal 
      which is uncountable.
      Then there exists a $\ka$-small $\infty$-category $D \map{sim}{} C$
      if and only if $hC$ is $\ka$-small and
      for every morphism $f : X \to Y$ in $C$,
      $\pi_0 C(X,Y)$ and $\pi_{i > 0}(C(X,Y) , f)$ are $\ka$-small.
      \begin{proof1}
        See Lurie HTT 5.4.1.2.
      \end{proof1}
    \end{lem}
    Since $h C(\omega)$ is small, in order to show $C(\om)$ is equivalent to
    a small $\infty$-category,
    it remains to show that for every morphism $f : X \to Y$ in $C$,
    $\pi_0 C(X,Y)$ and $\pi_{i > 0}(C(X,Y) , f)$ are small. 
    We have $\pi_0 (X , Y) = hC(X , Y)$ is small by assumption.
    For the higher homotopy groups, note that 
    $C(X,Y) \simeq \Om C(\Om X , Y)$ therefore
    the we can WLOG assume $f = 0$ for computation of the higher homotopy groups.
    Then $\pi_{i > 0}(C(X,Y), 0) \simeq h C(X[i] , Y)$ which is small again.

    
  \end{proof}

  \item An important example of a compactly generated stable $\infty$-category
  is $\VEC$.

  \begin{prop}
    
    Let $k$ be a field.
    Then there exists an $\infty$-category $\VEC$ called
    the \emph{right derived $\infty$-category of $k$-vector spaces} 
    with the following properties : 
    \begin{itemize}
      \item (Lurie HA 1.3.2.18) $\VEC$ is stable. 
      \item (Lurie HA 1.3.4.4 - Universal Property as Localisation) 
      There is a functor $l : \CH^-(k) \to \VEC$
      with the property that for all $\infty$-categories $E$,
      restricting along $l$ yields a fully faithful functor
      $\FUN(\VEC , E) \to \FUN(\CH^-(k) , E)$
      with essential image consisting of functors $\CH^-(k) \to E$
      which invert quasi-isomorphisms.
      \item (Lurie HA 1.3.2.9)
      $h\VEC$ gives the usual 1-category right derived category
      of $k$-vector spaces.
      
      Consequently, for $X, Y \in \CH^-(k)$,
      we have \[
        \pi_n \VEC(X,Y) = \pi_0 \Om^n \VEC(X,Y)
        \simeq \pi_0 \VEC(X , Y[n]) =: \EXT^n(X,Y)
      \]
    \end{itemize}
  \end{prop}

  \item $1\dash\CAT^\mathrm{ex}_\mathrm{cts}$ 
  has symmetric monoidal structure $\otimes$
  via the \emph{Lurie tensor product}. 

  We won't really need to know anything about the tensor product
  other than its universal property. 

  (IP : Explain how practically speaking, 
  it suffices to know the univeral property
  because we will work with compactly generated dg-categories,
  meaning computation will come down to
  compact generators and their homs.)

  (IP : Give impression of symmetric monoidal infinity categories via
  Lawvere theory perspective.)

  \textbf{
  Unanswered Q : is this only used because
  the theory of commutative dg-algebras compromises in positive characteristic?
  }
  \textbf{
    A : No. Characteristic zero is also used later in equivalence of
    Lie algebras and formal moduli problems.
    But I have no time to look into this.
  }

  \item $(\VEC, \otimes)$ 
  is the stable symmetric monoidal (right bounded) derived infinity category of 
  complexes of $k$-vector spaces.
  Its homotopy category $h(\VEC)$ is 1-categorical localisation of 
  the category of complexes of $k$-vectors spaces at quasi-isomorphisms,
  and has the usual $t$-structure.
  The heart of $\VEC$ is the usual abelian category of $k$-vector spaces.
  We use cohomological degree,
  where negative cohomological degree refers to homological degree.

  Practically speaking, 
  computations tensor product are done by using the projective model structure 
  on the category of complexes of $k$-vectors spaces.

  \item $(\VEC,\otimes)$ can be seen as an commutative algebra object in 
  the symmetric monoidal infinity category $1\dash\CAT^{st,cocompl}_{cts}$.
  Then $\DGCAT_{cts}$ denotes the infinity category of 
  left modules over $\VEC$ inside $(\infty,1)\dash\CAT^\EX_\CTS$.

  \item IP : derived rings stuff - Lurie HTT 5.5.9.3
  \item IP :  modules over derived rings as 
  symmetric monoidal $\infty$-cat - Lurie HA 7.1.2.13.
  Subtlety about different model structures is Lurie HA 7.1.2.9.

\end{itemize}

\end{document}